---
title: "Homework 1"
output: github_document
---

## Problem 1

```{r}
library(moderndive)
```
```{r}
library(tidyverse) 
```
Here I loaded the library moderndive to allow me to load the dataset and tidyverse
to be able to use the pull functions when calculating mean.

```{r}
data("early_january_weather")
```

I loaded the dataset above

The variable names in this dataset are `r names(early_january_weather)`.
The dataset has `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables.
The mean of the temperature in the dataset is `r mean(pull(early_january_weather, temp))`.
The numeric values of variables in this dataset are `r skimr::skim(early_january_weather)`

I used inline code to identify the variable names, numerical values, size of the data set,
and mean of the temperature variable.

```{r}
    ggplot(early_january_weather, aes(x=time_hour, y=temp, color=humid)) + geom_point()
ggsave("hw1plot.pdf", height = 4, width = 6) 
```

I created this plot of time vs temp and used color to depict humditiy levels. I then saved it as a pdf. In this plot, you can see that as the time_hour increases the temperature generally increases in a zig-zag pattern, with the exception of a sudden drop at the end.

## Problem 2

```{r}
hw1_df=
  tibble(
    numeric_samp = rnorm(10),
    greater_0 = numeric_samp > 0,
    vec_char = c("My", "homework", "assignment", "should", "have", "a", "character", "length", "of", "ten"),
    vec_factor = factor (c("low", "low", "low", "medium", "medium", "medium", "high", "high", "high", "high"))
  )
```

I created a data frame with a character vector length of 10, a factor vector length of 10 and 3 factor levels, a random sample size of 10 from a standard normal distribution, and a logical vector that indicated whether elements of the sample are greater than 0.

The mean of the random sample in my new dataframe is `r mean(pull(hw1_df, numeric_samp))`.

The mean of the logical variable in my new dataframe is `r mean(pull(hw1_df, greater_0))`.

The mean of the character variable in my new dataframe is `r mean(pull(hw1_df, vec_char))`.

The mean of the factor variable in my new dataframe is `r mean(pull(hw1_df, vec_factor))`.

I used inline code to pull the vectors out of the dataframe and take the mean of them. Taking the mean of random and logical variables work, but taking the mean of character and factor variables do not.

```{r results = "hide"}
as.numeric(pull(hw1_df,greater_0))
as.numeric(pull(hw1_df,vec_char))
as.numeric(pull(hw1_df,vec_factor))
```

I used the as.numeric function and used results=hide to hide the output but allow the code to run and be seen. When I used the as.numeric function, it converts the logical variables and factor variables to numerical values, but leaves the character variables as "NA". This explains why the mean of my character variables was NA. I noted that for my factor variables it assigned 3 of the same number for low, 3 of the same number for medium, and 4 of the same number for high when converting to numeric values. I also noted that my logical variables consisted of only 0s and 1s, which explains why the mean for my logical variables was between 0 and 1.