---
title: "homework 1"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(moderndive)
```
```{r echo = FALSE}
library(tidyverse) 
```

```{r}
data("early_january_weather")
```


The variable names in this dataset are `r names(early_january_weather)`.
The dataset has `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables.
The mean of the temperature in the dataset is `r mean(pull(early_january_weather, temp))`.

```{r}
    ggplot(early_january_weather, aes(x=time_hour, y=temp, color=humid)) + geom_point()
ggsave("hw1plot.pdf", height = 4, width = 6) 
```

In this plot, you can see that as the time_hour increases the temperature generally increases in a zig-zag pattern, with the exception of a sudden drop at the end.

```{r}
hw1_df=
  tibble(
    numeric_samp = rnorm(10),
    greater_0 = numeric_samp > 0,
    vec_char = c("My", "homework", "assignment", "should", "have", "a", "character", "length", "of", "ten"),
    vec_factor = factor (c("low", "low", "low", "medium", "medium", "medium", "high", "high", "high", "high"))
  )
```

The mean of the random variables in my new dataframe is `r mean(pull(hw1_df, numeric_samp))`.

The mean of the logical variables in my new dataframe is `r mean(pull(hw1_df, greater_0))`.

The mean of the character variables in my new dataframe is `r mean(pull(hw1_df, vec_char))`.

The mean of the factor variables in my new dataframe is `r mean(pull(hw1_df, vec_factor))`.

Taking the mean of random and logical variables work, but taking the mean of character and factor variables do not.



