---
title: "Homework 1"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r}
library(moderndive)
```
```{r}
library(tidyverse) 
```

```{r}
data("early_january_weather")
```


The variable names in this dataset are `r names(early_january_weather)`.
The dataset has `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables.
The mean of the temperature in the dataset is `r mean(pull(early_january_weather, temp))`.

```{r}
    ggplot(early_january_weather, aes(x=time_hour, y=temp, color=humid)) + geom_point()
ggsave("hw1plot.pdf", height = 4, width = 6) 
```

In this plot, you can see that as the time_hour increases the temperature generally increases in a zig-zag pattern, with the exception of a sudden drop at the end.

## Problem 2

```{r}
hw1_df=
  tibble(
    numeric_samp = rnorm(10),
    greater_0 = numeric_samp > 0,
    vec_char = c("My", "homework", "assignment", "should", "have", "a", "character", "length", "of", "ten"),
    vec_factor = factor (c("low", "low", "low", "medium", "medium", "medium", "high", "high", "high", "high"))
  )
```

The mean of the random sample in my new dataframe is `r mean(pull(hw1_df, numeric_samp))`.

The mean of the logical variable in my new dataframe is `r mean(pull(hw1_df, greater_0))`.

The mean of the character variable in my new dataframe is `r mean(pull(hw1_df, vec_char))`.

The mean of the factor variable in my new dataframe is `r mean(pull(hw1_df, vec_factor))`.

Taking the mean of random and logical variables work, but taking the mean of character and factor variables do not.

```{r results = "hide"}
as.numeric(pull(hw1_df,greater_0))
as.numeric(pull(hw1_df,vec_char))
as.numeric(pull(hw1_df,vec_factor))
```

When I used the as.numeric function, it converts the logical variables and factor variables to numerical values, but leaves the character variables as "NA". This explains why the mean of my character variables was NA. I noted that for my factor variables it assigned 3 of the same number for low, 3 of the same number for medium, and 4 of the same number for high when converting to numeric values. I also noted that my logical variables consisted of only 0s and 1s, which explains why the mean for my logical variables was between 0 and 1.